Analytic Doppler Imaging

### 2019-08-22 tex/gitlinks.tex
increased line width to match Vogt1987

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/3bca8febf1e8738da63bacbc3959e6442e52272c/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/3bca8febf1e8738da63bacbc3959e6442e52272c/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/3bca8febf1e8738da63bacbc3959e6442e52272c/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/user/repo/_build}{#1}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/076a0d29804b1875a480b0fd74a7ea6738368263/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/076a0d29804b1875a480b0fd74a7ea6738368263/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/076a0d29804b1875a480b0fd74a7ea6738368263/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/user/repo/_build}{#1}}

### 2019-08-22 tex/ms.tex
increased line width to match Vogt1987

\newcommand{\R}{\bvec{R}}
\newcommand{\AOne}{\bvec{A_1}}
\newcommand{\alm}{\bvec{a}}
\newcommand{\x}{\bvec{x}}

\newcommand{\D}{D}
\newcommand{\Doppler}{\bvec{D}}
\newcommand{\Surf}{\mathcal{S}}
\newcommand{\Curve}{\mathcal{C}}
\newcommand{\Dargs}{\bvec{d}}
\newcommand{\lmax}{\ensuremath{l_\mathrm{max}}}
\newcommand{\spot}{\texttt{SPOT}\xspace}

\newcommand{\kT}{\boldsymbol{\kappa}^\top}
\newcommand{\rhoT}{\boldsymbol{\rho}^\top}
\newcommand{\ylmbasis}{\boldsymbol{\psi}^\top}
\newcommand{\pbasis}{\boldsymbol{\phi}^\top}
\newcommand{\pbasisn}{\ensuremath{\phi_n}}

\newcommand{\azero}{\ensuremath{\bvec{a_0}}}

@@

\begin{abstract}
We derive a closed form, analytic solution to the problem of Doppler imaging
of stellar surfaces in the limit of negligible differential rotation and
convective blueshift. The model for the observed spectrum is linear in 
both the unbroadened spectrum and the surface map of the star, provided the
latter is expressed as a sum of spherical harmonics. As a result, the 
posterior distributions of both the unbroadened spectrum and the stellar map
conditioned on each other have a closed form, analytic solution that is 
computationally trivial to evaluate. When neither the unbroadened spectrum
nor the stellar map is known a priori, the global optimum can usually be
found via a fast iterative approach that also yields a lower bound on the
uncertainties.
%
\href{https://github.com/rodluger/paparazzi}{\color{linkcolor}\faGithub}
\figtime{allfigures}
\end{abstract}

%
\section{Introduction}
%
Check out \citet{Luger2019} and \citet{Bedell2019} and stuff.
%
All figures in this paper include links {\color{linkcolor}\faFileCodeO}
to the \Python scripts that generated them. These figures were auto-generated
using the 
\href{https://dev.azure.com/rodluger/paparazzi/_build}{Azure Pipelines}
continuous integration (CI) service, and
icons next to each caption \figtimebox{XXmYYs} indicate the runtime
for each figure. The total runtime for the generation of this paper is
displayed above, at the end of the abstract.

%
\section{The problem}
\label{sec:the_problem}
%
Let $I(\lnlam, \x, t, \Dargs)$ be the specific 
intensity observed 
at log wavelength $\lnlam \equiv \ln\lambda$ and at sky-projected 
Cartesian position $\x = (x, y, z)$ on the surface of the 
star at time $t$, where
$\Dargs$ is a set of arbitrary parameters of the Doppler field.
We may express this intensity as
%
\begin{align}
    \label{eq:the_problem:Ixi}
    I(\lnlam, \x, t, \Dargs) &= 
        I\Big(\lnlam_0 + \D(\x, \Dargs), \x, t\Big)
\end{align}
%
where $\lnlam_0$ is the log wavelength in the rest frame and $\D$ is
the Doppler shift in log wavelength space:
%
\begin{align}
    \label{eq:the_problem:D}
    \D(\x, \Dargs) 
        &=
        \frac{1}{2}\ln\left( 
            \frac{1 + \beta(\x, \Dargs)}{1 - \beta(\x, 
            \Dargs)} 
        \right)
\end{align}
%
where $\beta = v(\x, \Dargs) / c$ is the ratio of the 
radial velocity at a point on the surface of the star to the speed of light.
In keeping with the literature, we take positive values of $v$ (and
$\D$) to mean redshifts.

@@

\section{The Solution}

@@

\subsection{Solution for the intensity}
\label{sec:solve_y}
For a fixed, spatially constant rest-frame spectrum $\bvec{s}$, the model
for the flux vector may be written as
%
\begin{align}
    \label{eq:inverse:fy}
    \bvec{f}
    &=
    \Doppler
    \,
    \bvec{S}
    \,
    \bvec{y}
    \quad,
\end{align}
%
where
%
\begin{align}
    \label{eq:inverse:S}
    \setstackgap{L}{1.25\baselineskip}
    \bvec{S} =
        \begin{pmatrix}
        \quadquad\bvec{s}\quadquad & &            &            &  \\
        & \quadquad\bvec{s}\quadquad &            &            &  \\
        &            & \quadquad\bvec{s}\quadquad &            &  \\
        &            &            & \quadquad\bvec{s}\quadquad &  \\
        &            &            &               & \ddots
        \end{pmatrix}
\end{align}
%
is a $(NK' \times N)$ block matrix constructed by repeating the column
vector $\bvec{s}$ $N$ times in blocks along the main diagonal. 
%
Before we solve this equation for $\bvec{y}$, we note that in practice
it is convenient to fix the coefficient of the $Y_{0,0}$ spherical
harmonic, $y_0$, to unity. After all, this coefficient is not directly
constrained by the data, as it merely sets the baseline intensity on the
surface of the star and is therefore formally degenerate with the stellar 
luminosity (which also cannot be directly inferred from the data). This
choice further ensures a mean baseline of unity for the model 
vector $\mathbf{f}$. We may therefore write
%
\begin{align}
    \label{eq:inverse:fy1}
    \bvec{f}
    &=
    \Doppler
    \,
    \bvec{s}_\bvec{0}
    \,
    +
    \,
    \Doppler
    \,
    \bvec{S_1}
    \,
    \bvec{y}_\bvec{1}
    \quad,
\end{align}
%
where the vector $\bvec{s_0}$ denotes the first column of $\bvec{S}$,
the matrix $\bvec{S_1}$ denotes the remaining columns of $\bvec{S}$, and
$\bvec{y_1}$ is the quantity we wish to solve for: the vector of spherical 
harmonic coefficients of degree $l \ge 1$.

@@

@@

The model remains linear in both the spherical harmonic coefficients and the
spectral components, and the procedures outlined in \S\ref{sec:inverse} may
still be followed to solve the inverse problem, provided we unroll these
matrices into vectors, letting
$\mathbf{s} = \mathrm{vec}(\boldsymbol{\mathbb{S}})$
and
$\mathbf{y} = \mathrm{vec}(\boldsymbol{\mathbb{Y}})$.
A detailed discussion of this general case is deferred to future work,
but we present an example of a two-component stellar spectrum in the
examples section below.

\section{The SPOT star}
\label{sec:spotstar}

\cite{Vogt1987}

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.85\linewidth]{figures/spot_setup.pdf}
    \oscaption{spot_setup}{%
        Setup for the \spot problem.
        \label{fig:spot_setup}
    }
    \end{centering}
\end{figure}

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.49\linewidth]{figures/spot_y1_timeseries.pdf}
    \includegraphics[width=0.49\linewidth]{figures/spot_y1_rect.pdf}
    \oscaption{spot_y1}{%
        Solution to the \spot problem at high SNR when both 
        the rest frame spectrum and the baseline are known.
        \label{fig:spot_y1}
    }
    \end{centering}
\end{figure}

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.49\linewidth]{figures/spot_y1b_timeseries.pdf}
    \includegraphics[width=0.49\linewidth]{figures/spot_y1b_rect.pdf}
    \\[0.5em]
    \includegraphics[width=0.405\linewidth]{figures/spot_y1b_baseline.pdf}
    \includegraphics[width=0.575\linewidth]{figures/spot_y1b_coeffs.pdf}
    \oscaption{spot_y1b}{%
        Similar to Figure~\ref{fig:spot_y1}, but assuming the baseline
        is not known.
        \label{fig:spot_y1b}
    }
    \end{centering}
\end{figure}

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_timeseries.pdf}
    \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_rect.pdf}
    \\[0.5em]
    \includegraphics[width=0.405\linewidth]{figures/spot_y1bs_baseline.pdf}
    \includegraphics[width=0.575\linewidth]{figures/spot_y1bs_coeffs.pdf}
    \\[0.5em]
    \includegraphics[width=0.98\linewidth]{figures/spot_y1bs_spectrum.pdf}
    \oscaption{spot_y1bs}{%
        Similar to Figure~\ref{fig:spot_y1}, but assuming we have no
        information about either the spectrum, the baseline, or the map
        coefficients.
        \label{fig:spot_y1bs}
    }
    \end{centering}
\end{figure}

\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=0.98\linewidth]{figures/inclinations.pdf}
    \oscaption{inclinations}{%
        Recovered \spot map as a function of inclination.
        \label{fig:inclinations}
    }
    \end{centering}
\end{figure}

\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=0.98\linewidth]{figures/snr.pdf}
    \oscaption{snr}{%
        Recovered \spot map as a function of SNR per resolution element.
        \label{fig:snr}
    }
    \end{centering}
\end{figure}

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/twospec.pdf}
    \oscaption{twospec}{%
        Learning two spectra simultaneously.
        \label{fig:twospec}
    }
    \end{centering}
\end{figure}

\section{Performance}
\label{sec:performance}
%
\xxx{In progress...}
Evaluation of the model via Equation~(\ref{eq:deconv:F}) requires 
first the rotation of the $(\lmax + 1)^2$
$\kT$ kernels (each of length $W$) to the correct stellar 
rotational phase, an operation that scales approximately
as $W \lmax^3$,
followed by $(\lmax + 1)^2$
linear convolutions of the rotated $\kT$ kernels with the 
spectral components (each of length $K$), which scales
approximately as $W K \lmax^2$. Since typically $K \gg \lmax$,
the latter computation dominates and the entire evaluation 
takes $\mathcal{O}(W K \lmax^2)$ operations.

\section{Stuff we're not addressing}
%
\xxx{In progress...}
Differential rotation and convective blueshift.

@@

    $\lambda$                & wavelength (in nm)                                    & \S\ref{sec:the_problem}\\
    $\lnlam$                 & $\ln\lambda$ (observer frame)                         & \S\ref{sec:the_problem}\\
    $\lnlam_0$               & $\ln\lambda$ (rest frame)                             & \S\ref{sec:the_problem}\\

>>>>

@@

\begin{abstract}
We derive a closed form, analytic solution to the problem of Doppler imaging
of stellar surfaces in the limit of negligible differential rotation and
convective blueshift. The model for the observed spectrum is linear in 
both the unbroadened spectrum and the surface map of the star, provided the
latter is expressed as a sum of spherical harmonics. As a result, the 
posterior distributions of both the unbroadened spectrum and the stellar map
conditioned on each other have a closed form, analytic solution that is 
computationally trivial to evaluate. When neither the unbroadened spectrum
nor the stellar map is known a priori, the global optimum can usually be
found via a fast iterative approach that also yields a lower bound on the
uncertainties.
\xxx{%
Data-driven modeling at its finest $\cdot$ %
Works on blended lines $\cdot$ %
Uses the whole spectrum $\cdot$ %
Uncertainties FTW $\cdot$ %
Probably works on slow rotators $\cdot$ %
Differentiable! $\cdot$ %
Fast! $\cdot$ %
Use in MCMC to marginalize over inclination and stuff $\cdot$ %
}
%
\href{https://github.com/rodluger/paparazzi}{\color{linkcolor}\faGithub}
\end{abstract}

%
\section{Introduction}
%
\xxx{Check out \citet{Luger2019} and \citet{Bedell2019} and stuff.}

The paper is organized as follows: in \S\ref{sec:the_problem}~and~%
\S\ref{sec:the_solution} we introduce the math behind the Doppler imaging
problem and derive a closed form expression for the model. In
\S\ref{sec:linear},~\S\ref{sec:inverse},~and~\S\ref{sec:bellswhistles} 
we demonstrate how to re-express 
the model as a linear operation on the input spectrum and stellar map and
derive closed form expressions for the two conditioned on the data and priors.
In \S\ref{sec:spotstar} we apply our techniques to a mock problem. We
further discuss and summarize our results in
\S\ref{sec:discussion}~and~\S\ref{sec:conclusions}. Finally, auxiliary
derivations are presented in the Appendix.

All figures in this paper include links {\color{linkcolor}\faFileCodeO}
to the \Python scripts that generated them. The figures were auto-generated
using the 
\href{https://dev.azure.com/rodluger/paparazzi/_build}{Azure Pipelines}
continuous integration (CI) service, running on
a two-core 2.3 GHz \texttt{Standard\_DS2\_v2} virtual machine with 6 GiB physical memory.
% https://docs.microsoft.com/en-us/azure/virtual-machines/windows/sizes-general#dsv2-series
We also include icons next to each caption \figtimebox{XXmYYs} that
indicate the total CPU time taken to generate each figure.

%
\section{The problem}
\label{sec:the_problem}
%
Let $I(\lnlam, \x, t, \Dargs)$ be the specific 
intensity observed 
at log wavelength $\lnlam \equiv \ln\nicefrac{\lambda}{\lambda_\mathrm{r}}$ 
and at sky-projected 
Cartesian position $\x = (x, y, z)$ on the surface of the 
star at time $t$, where
$\Dargs$ is a set of arbitrary parameters of the Doppler field
and $\lambda_\mathrm{r}$ is a reference wavelength.
We may express this intensity as
%
\begin{align}
    \label{eq:the_problem:Ixi}
    I(\lnlam, \x, t, \Dargs) &= 
        I\Big(\lnlam_0 + \D(\x, \Dargs), \x, t\Big)
\end{align}
%
where $\lnlam_0$ is the log wavelength in the rest frame and $\D$ is
the Doppler shift in log wavelength space:
%
\begin{align}
    \label{eq:the_problem:D}
    \D(\x, \Dargs) 
        &=
        \frac{1}{2}\ln\left( 
            \frac{1 + \beta(\x, \Dargs)}{1 - \beta(\x, 
            \Dargs)} 
        \right)
\end{align}
%
where $\beta = v(\x, \Dargs) / c$ is the ratio of the 
radial velocity at a point on the surface of the star to the speed of light.
In keeping with the literature, we take positive values of $v$ (and
$\D$) to mean redshifts.

@@

\section{The Solution}
\label{sec:the_solution}

@@

\subsection{Solution for the map}
\label{sec:solve_y}
For a fixed, spatially constant rest-frame spectrum $\bvec{s}$, the model
for the flux vector may be written as
%
\begin{align}
    \label{eq:inverse:fy}
    \bvec{f}
    &=
    \Doppler
    \,
    \bvec{S}
    \,
    \bvec{y}
    \quad,
\end{align}
%
where
%
\begin{align}
    \label{eq:inverse:S}
    \setstackgap{L}{1.25\baselineskip}
    \bvec{S} =
        \begin{pmatrix}
        \quadquad\bvec{s}\quadquad & &            &            &  \\
        & \quadquad\bvec{s}\quadquad &            &            &  \\
        &            & \quadquad\bvec{s}\quadquad &            &  \\
        &            &            & \quadquad\bvec{s}\quadquad &  \\
        &            &            &               & \ddots
        \end{pmatrix}
\end{align}
%
is a $(NK' \times N)$ block matrix constructed by repeating the column
vector $\bvec{s}$ $N$ times in blocks along the main diagonal. 
%
Before we solve this equation for $\bvec{y}$, we note that in practice
it is convenient to fix the coefficient of the $Y_{0,0}$ spherical
harmonic, $y_0$, to unity. After all, this coefficient is not directly
constrained by the data, as it merely sets the baseline intensity on the
surface of the star and is therefore formally degenerate with the stellar 
luminosity (which also cannot be directly inferred from the data). This
choice further ensures a mean baseline of unity for the model 
vector $\mathbf{f}$. We may therefore write
%
\begin{align}
    \label{eq:inverse:fy1}
    \bvec{f}
    &=
    \Doppler
    \,
    \bvec{s}_\bvec{0}
    \,
    +
    \,
    \Doppler
    \,
    \bvec{S_1}
    \,
    \bvec{y}_\bvec{1}
    \quad,
\end{align}
%
where the vector $\bvec{s_0}$ denotes the first column of $\bvec{S}$,
the matrix $\bvec{S_1}$ denotes the remaining columns of $\bvec{S}$, and
$\bvec{y_1}$ is the quantity we wish to solve for: the vector of spherical 
harmonic coefficients of degree $l \ge 1$.

@@

Before we demonstrate our formalism in practice, we consider three
modifications to our model that are often required when modeling real
data. Below we discuss what to do when the relative brightness of the
star across different observations is unknown (\S\ref{sec:norm}), how
to account for the effects of limb darkening (\S\ref{sec:ld}), and how
to model stars whose local spectra differ within and outside of starspots
(\S\ref{sec:eigen}).

@@

The model remains linear in both the spherical harmonic coefficients and the
spectral components, and the procedures outlined in \S\ref{sec:inverse} may
still be followed to solve the inverse problem, provided we unroll these
matrices into vectors, letting
$\mathbf{s} = \mathrm{vec}(\boldsymbol{\mathbb{S}})$
and
$\mathbf{y} = \mathrm{vec}(\boldsymbol{\mathbb{Y}})$.
A detailed discussion of this general case is deferred to future work,
but we present an example of a two-component stellar spectrum in the
following section.

\section{Application to a spotted star}
\label{sec:spotstar}

In this section we apply the formalism developed in \S\ref{sec:inverse}
and \S\ref{sec:bellswhistles} to a synthetic dataset of a rapidly
rotating spotted star. This section is motivated by the
examples in \cite{Vogt1987}, who generated rotationally-broadened spectra
of a rapidly-rotating star with the letters ``VOGT'' painted across 
the northern hemisphere. In that paper, the authors
generated synthetic line profiles of the Fe I 
$\lambda 6430$ absorption line with equivalent width $W \approx 10$~km/s
and from these computed rotationally broadened spectra for a star at an 
inclination $i=40^\circ$ rotating at projected velocity $v\sin i = 40$~km/s.
The spectra were computed at 16 equally spaced rotational phases and
downsampled to 32 wavelength bins per epoch, for a total of 512 data
points.

We generated our spectrum at high resolution 
($R \equiv \frac{\lambda}{\Delta\lambda} = 300,000$)
centered at a reference wavelength $\lambda_\mathrm{r} = 6430$ nm.
The spectrum consists of a Gaussian absorption line in log-wavelength
($\lnlam$) space with amplitude $0.5$ and standard deviation 
$\sigma_{\lnlam} = 1.4\times 10^{-5}$. This corresponds to a FWHM of about
$2.355~\sigma_{\lnlam}~\lambda_\mathrm{r}~\approx~0.2$ nm or, in velocity space,
$2.355~\sigma_{\lnlam}~c~\approx~10$ km/s, equal to the value used in
\citet{Vogt1987}. Unlike \citet{Vogt1987}, we add 20 additional small
absorption lines at random positions throughout the spectrum, all of 
the same FWHM but of varying depths, including some line blends. In total,
our spectrum consists of $K = 201$ log-wavelength bins in the range
$-3.3\times 10^{-4} < \lnlam < 3.3\times 10^{-4}$ plus an additional
%
\begin{align}
    W - 1 &= \frac{40~\mathrm{km/s}}{c} \frac{201}{3.3 \times 10^{-4}} - 1 \nonumber \\
          &= 80
\end{align}
%
log-wavelength bins of padding (40 on either side) to eliminate edge
effects due to the convolution. As in \citet{Vogt1987},
we assume a projected velocity of $v\sin i = 40$ km/s and an inclination
$i = 40^\circ$.

% Our default SNR is about 75.

Recover images with an effective resolution of $12^\circ$.

\begin{figure}[t!]
    \begin{centering} 
    \includegraphics[width=0.85\linewidth]{figures/spot_setup.pdf}
    \oscaption{spot_setup}{%
        The basic setup for the \spot problem. We compute the 
        $l_\mathrm{max} = 15$ spherical harmonic expansion of 
        a map where the word ``SPOT'' has been placed across the northern 
        hemisphere (top left). Each point on the surface is
        given the same spectrum, composed of a sum of synthetic 
        Gaussian absorption lines (top right). The specific intensity
        at each point on the surface is equal to this spectrum weighted
        by the intensity of the map, which is close to zero within the
        spot (point labeled \texttt{B}) and close ot unity 
        outside the spot (point labeled \texttt{A}).
        %
        To generate the synthetic dataset, the star is inclined at
        $40^\circ$ with respect to the line of sight and the disk-integrated
        spectrum is computed at 16 equally-spaced phases between
        $-180^\circ$ and $180^\circ$ (lower panel).
        %
        \label{fig:spot_setup}
    }
    \end{centering}
\end{figure}

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.49\linewidth]{figures/spot_y1_timeseries.pdf}
    \includegraphics[width=0.49\linewidth]{figures/spot_y1_rect.pdf}
    \oscaption{spot_y1}{%
        The solution to the \spot problem at high SNR when both 
        the rest frame spectrum and the baseline are known.
        The panel on the left shows the inferred map at each of the 16
        epochs, alongside the observed spectrum (black points) and the
        best-fit model (orange lines). The rectangular projection of the
        original map is shown at the top right; the inferred map is
        displayed below it. The bottom panel shows the posterior uncertainty
        as a function of latitude and longitude, ranging from close to zero
        in the northern hemisphere to $\sigma_\mathrm{prior} \approx 10\%$
        below a latitude of $-30^\circ$. The latter is the uncertainty
        associated with our particular choice of prior, as the southernmost
        latitudes of the star are never visible to the observer.
        \label{fig:spot_y1}
    }
    \end{centering}
\end{figure}

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.49\linewidth]{figures/spot_y1b_timeseries.pdf}
    \includegraphics[width=0.49\linewidth]{figures/spot_y1b_rect.pdf}
    \\[0.5em]
    \includegraphics[width=0.405\linewidth]{figures/spot_y1b_baseline.pdf}
    \includegraphics[width=0.575\linewidth]{figures/spot_y1b_coeffs.pdf}
    \oscaption{spot_y1b}{%
        Similar to Figure~\ref{fig:spot_y1}, but assuming the baseline
        is not known. The panel at the bottom left shows the true baseline
        (blue) and the inferred baseline (orange), along with its $1\sigma$
        uncertainty. The large offset between the two highlights one of the
        fundamental degeneracies of the problem: since most of the southern
        hemisphere of the star is never visible, the coefficient of the
        $Y_{1,-1}$
        (\raisebox{-0.2em}{\includegraphics[width=1em]{figures/Y1m1.pdf}})
        spherical harmonic is not constrained by the data, resulting in 
        an unknowable additive offset in the baseline.
        This effect can be seen also in (\emph{a}) the inferred map, 
        where the background 
        intensity in the northern hemisphere is significantly larger than 
        that in the southern hemisphere, and (\emph{b}) the spherical
        harmonic coefficients (bottom right), where a large discrepancy is
        visible between the true and inferred values of the first two
        coefficients.
        \label{fig:spot_y1b}
    }
    \end{centering}
\end{figure}

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_timeseries.pdf}
    \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_rect.pdf}
    \\[0.5em]
    \includegraphics[width=0.405\linewidth]{figures/spot_y1bs_baseline.pdf}
    \includegraphics[width=0.575\linewidth]{figures/spot_y1bs_coeffs.pdf}
    \\[0.5em]
    \includegraphics[width=0.98\linewidth]{figures/spot_y1bs_spectrum.pdf}
    \oscaption{spot_y1bs}{%
        Similar to Figure~\ref{fig:spot_y1}, but assuming we have no
        information about either the spectrum, the baseline, or the map
        coefficients. The bottommost panel now shows the true rest frame
        spectrum (blue line), the initial guess based on a deconvolution
        (dotted orange line), and the inferred spectrum (orange line, with
        shaded $1\sigma$ uncertainty). The grey regions indicate wavelength
        regions outside the observation window, but whose features still
        contribute to the observed spectrum due to rotational broadening.
        \label{fig:spot_y1bs}
    }
    \end{centering}
\end{figure}

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.98\linewidth]{figures/inclinations.pdf}
    \oscaption{inclinations}{%
        Recovered \spot map as a function of stellar inclination. The
        rest frame spectrum is assumed to be known exactly, but the
        baseline is not. At very low inclinations, the small
        projected velocities begin to degrade the spatial resolution of
        the inferred map, while at inclinations close to $90^\circ$ there
        is a degeneracy between the northern and southern hemispheres.
        \label{fig:inclinations}
    }
    \end{centering}
\end{figure}

\begin{figure}[p!]
    \begin{centering}
    \includegraphics[width=0.98\linewidth]{figures/snr.pdf}
    \oscaption{snr}{%
        Recovered \spot map as a function of SNR per resolution element.
        The quality of the inferred map in the northern hemisphere improves
        with SNR, but at very high SNR the region surrounding the global
        optimum becomes so small that our optimization methods struggle to
        converge on the correct solution.
        \label{fig:snr}
    }
    \end{centering}
\end{figure}

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/twospec.pdf}
    \oscaption{twospec}{%
        An example of a star whose spectrum is different within the spot
        (\texttt{B}) and outside of the spot (\texttt{A}). Everywhere on 
        the surface, the spectrum is a linear combination of two
        ``eigenspectra'' ($s_1$ and $s_2$).
        As in Figure~\ref{fig:spot_y1bs}, we assume
        we do not know the map, the baseline, or either of the eigenspectra.
        The top row shows the true values for the map and the spectra, and
        the bottom row shows our inferred values.
        \label{fig:twospec}
    }
    \end{centering}
\end{figure}

\section{Discussion}
\label{sec:discussion}
%
\xxx{In progress...}
Evaluation of the model via Equation~(\ref{eq:deconv:F}) requires 
first the rotation of the $(\lmax + 1)^2$
$\kT$ kernels (each of length $W$) to the correct stellar 
rotational phase, an operation that scales approximately
as $W \lmax^3$,
followed by $(\lmax + 1)^2$
linear convolutions of the rotated $\kT$ kernels with the 
spectral components (each of length $K$), which scales
approximately as $W K \lmax^2$. Since typically $K \gg \lmax$,
the latter computation dominates and the entire evaluation 
takes $\mathcal{O}(W K \lmax^2)$ operations.

\xxx{We are not addressing differential rotation and convective blueshift.}
\xxx{Telluric lines could be treated much as in Figure~\ref{fig:twospec}.}
\xxx{Instrumental profile is another Toeplitz matrix.}

\section{Conclusions}
\label{sec:conclusions}
\xxx{Hello.}

@@

    $\lambda$                & wavelength                                            & \S\ref{sec:the_problem}\\
    $\lambda_\mathrm{r}$     & reference wavelength                                  & \S\ref{sec:the_problem}\\
    $\lnlam$                 & $\ln\nicefrac{\lambda}{\lambda_\mathrm{r}}$ (observer frame)  & \S\ref{sec:the_problem}\\
    $\lnlam_0$               & $\ln\nicefrac{\lambda}{\lambda_\mathrm{r}}$ (rest frame)      & \S\ref{sec:the_problem}\\
